---
title: "worksheet#4"
author: "Missy Key Sadsad"
date: "2023-11-08"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

library(ggplot2)


#Using Loop Function

1. Using the for loop, create an R script that will display a 5x5 matrix as shown in
Figure 1. It must contain vectorA = [1,2,3,4,5] and a 5 x 5 zero matrix.

```{r}
vectorA <- c(1, 2, 3, 4, 5)
matrixA <- matrix(0, nrow = 5, ncol = 5)

matrixA

 for (i in 1:5) {
  for (j in 1:5) {
    matrixA[i, j] <- abs(vectorA[i] - vectorA[j])
  }
}

matrixA

```

2. Print the string "*" using for() function. The output should be the same as shown
in Figure
```{r} 
rightTriangle <- c()  
for(i in 1:5) {                                             
   for(j in 1:i+1) {  
      rightTriangle = c(rightTriangle, "*")  
   }  
   print(rightTriangle)
   rightTriangle <- c()  
}
```
3. Get an input from the user to print the Fibonacci sequence starting from the 1st input
up to 500. Use repeat and break statements. Write the R Scripts and its output.
```{r}

 n <- as.integer(readline(prompt = "Enter the number of terms: "))

a <- 0
b <- 1

cat("Fibonacci Sequence:", a, b)

# Generate the sequence
repeat {
  c <- a + b
  if (c > 500) {
    break
  }
  cat(", ",c)
  a <- b
  b <- c
}

```


#Using Basic Graphics (plot(),barplot(),pie(),hist())

4. Import the dataset as shown in Figure 1 you have created previously.

a. What is the R script for importing an excel or a csv file? Display the first 6 rows of
the dataset? Show your codes and its result.

```{r}
HouseholdData <-read.table("HouseholdData.csv",header = TRUE, sep = ",", as.is = TRUE)
View(HouseholdData)

head(HouseholdData,6)
```
b. Create a subset for gender(female and male). How many observations are there in
Male? How about in Female? Write the R scripts and its output.

```{r}
male_subset <- subset(HouseholdData, Gender == 'M')
female_subset <- subset(HouseholdData, Gender == 'F')

male_count <- nrow(male_subset)
male_count

female_count <- nrow(female_subset)
female_count


```

c. Create a graph for the number of males and females for Household Data. Use plot(),
chart type = barplot. Make sure to place title, legends, and colors. Write the R scripts and
its result.

```{r}
count <- c(male_count, female_count)
gender <- c("Male", "Female")

barplot(count, 
        names.arg = gender,
        main = "The number of Males and Females in Household Data",
        xlab = "Gender",
        ylab = "Count",
        col = c("blue", "pink"))
legend("topright",
       legend = gender,
       fill = c("blue", "pink"))
```
5. The monthly income of Dela Cruz family was spent on the following:

a. Create a piechart that will include labels in percentage.Add some colors and title of
the chart. Write the R scripts and show its output.
```{r}
monthly_income <- c(60,10,5,25)

pie(monthly_income,
    main = "Monthly Income of Dela Cruz family",
    col = rainbow(length(monthly_income)),
    labels = c("Food", "Electricity", "Savings", "Miscellaneous")
    )

```
6. Use the iris dataset.

a. Check for the structure of the dataset using the str() function. Describe what you
have seen in the output.
```{r}
data(iris)

str(iris)

#the str(iris) output gives us a clear overview of the structure of the Iris dataset, including the number of observations, variables, and their respective data types.
```



