---
title: "Worksheet-4c in R"
author: "Missy Key Sadsad BSIT-2B"
date: "2023-11-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1. Use the dataset mpg
a. Show your solutions on how to import a csv file into the environment.

```{r}

#a
mpg <-read.csv(file = "mpg.csv",header = TRUE, sep = "," )
View(mpg)

#b
str(mpg)

#c
#based on given its class, fl,drv,model,manufacturer
```



2. Which manufacturer has the most models in this data set? Which model has the most variations?
Show your answer.


```{r}

#a
manufacturers <- table(mpg$manufacturer)
manufacturers #dodge

library(dplyr)

#b
models <- mpg%>%count(mpg$model)
models #caravan 2wd

unique_models <- mpg %>%group_by(manufacturer)%>%distinct(model)
unique_models


library(ggplot2)

qplot(manufacturer, data = mpg,
    geom = "bar", fill = manufacturer)
 

```


2. Same dataset will be used. You are going to show the relationship of the modeland the manufacturer.


```{r}
#a
ggplot(mpg, aes(model, manufacturer)) + geom_point()

#b based on the graph, it created a simple scatterplot where each point represent the manufacturer and its model.

```

3. Plot the model and the year using ggplot(). Use only the top 20 observations. Write the codes and
its results.

```{r}

top_20_observations <- head(mpg, 20)
 

ggplot(top_20_observations, aes(x = model, y = year)) 
```

4. Using the pipe (%>%), group the model and get the number of cars per model. Show codes and its result
```{r}
models_group <- mpg %>%group_by(manufacturer)
models_group

#a 
```