---
title: "Worksheet-4c in R"
author: "Missy Key Sadsad BSIT-2B"
date: "2023-11-22"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1. Use the dataset mpg
a. Show your solutions on how to import a csv file into the environment.

```{r}

#a
mpg <-read.csv(file = "mpg.csv",header = TRUE, sep = "," )
View(mpg)

#b
str(mpg)

#c
#based on given its displ, cty,hwy 
```



2. Which manufacturer has the most models in this data set? Which model has the most variations?
Show your answer.


```{r}

#a
manufacturers <- table(mpg$manufacturer)
manufacturers #dodge

library(dplyr)

#b
models <- mpg%>%count(mpg$model)
models #caravan 2wd

unique_models <- mpg %>%group_by(manufacturer)%>%distinct(model)
unique_models


library(ggplot2)

qplot(manufacturer, data = mpg,
    geom = "bar", fill = manufacturer)
 

```


2. Same dataset will be used. You are going to show the relationship of the modeland the manufacturer.


```{r}
#a
ggplot(mpg, aes(model, manufacturer)) + geom_point()

#b 
#based on the graph, it created a simple scatterplot where each point represent the manufacturer and its model.

```

3. Plot the model and the year using ggplot(). Use only the top 20 observations. Write the codes and
its results.

```{r}
#3.
top_20_observations <- head(mpg, 20)

ggplot(top_20_observations, aes(x = model, y = year)) 
```

4. Using the pipe (%>%), group the model and get the number of cars per model. Show codes and its result
```{r}




library(dplyr)

models_group <- mpg %>%
group_by(model)%>% 
summarise(number_of_cars = n())
models_group

 

 
#a
ggplot(top_20_observations, aes(x = model)) +
  geom_bar(fill = "blue", alpha = 0.5) +  
  labs(title = "Top 20 Observations",
       x = "Car Model",
       y = "Numbers of Car") +
  theme_minimal()

#b
ggplot(top_20_observations, aes(x = model)) +
  geom_bar(fill = "skyblue", alpha = 0.7) +  # You can customize the color and transparency
  labs(title = "Top 20 Observations",
       x = "Car Model",
       y = "Numbers of Car") +
  theme_minimal() +
  coord_flip()



```


5. Plot the relationship between cyl - number of cylinders and displ - engine displacement using
geom_point with aesthetic color = engine displacement. Title should be “Relationship between
No. of Cylinders and Engine Displacement”.
 
```{r}
ggplot(mpg, aes(x = cyl, y = displ, color = displ)) +
  geom_point() +
  labs(title = "Relationship between No. of Cylinders and Engine Displacement",
       x = "Number of cyl",
       y = "Number of displ") +
  scale_color_continuous(name = "Engine Displacement") +
  theme_minimal()

#a
#this code will generate a scatter plot with a trendline, allowing you to observe any patterns in the relationship between the number of cylinders and engine displacement. Adjustments can be made based on your specific needs and preferences.


```

6. Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon). Mapped
it with a continuous variable you have identified in #1-c. What is its result? Why it produced such
output?


```{r}
ggplot(mpg, aes(x = displ, y = hwy, color = cty)) +
geom_point() +
  labs(title = "Relationship between Engine Displacement and Highway MPG",
       x = "Engine Displacement",
       y = "Highway MPG",
       color = "City MPG") +
  theme_minimal()
```

6. Import the traffic.csv onto your R environment.


```{r}
#a
traffic_data <- read.csv("traffic.csv")
View(traffic_data)

num_traffic_obv <-nrow(traffic_data) 
num_traffic_obv

str(traffic_data)
#The variable of traffic dataset is DateTime, Junction, Vehicles, and ID.
 
#b

#c
```

7. From alexa_file.xlxs, import it to your environment
```{r}
library(readxl)
alexa_file <- read_excel("~/GitHub/RWorksheets_Sadsad/Worksheet#4/RWorksheet#4b/alexa_file.xlsx")
View(alexa_file)

#a
nrow(alexa_file)
ncol(alexa_file)

#b
alexa_data <- alexa_file%>%
  group_by(variation) %>%
  summarise(Frequency = n())

View(alexa_data)

ggplot(alexa_data, aes(x = variation, y = Frequency )) +
  geom_bar(stat = "identity")  +
   labs(
    title = "Variations of Alexa Devices",
    x = "Variation",
    y = "Frequency"
  )

#b
#Each bar represents a variation, and its height indicates how frequently it appears in the data. This visual quickly highlights the more and less common variations.

#c
summary_reviews <- alexa_file %>%
  group_by(date) %>%
  summarize(NumVerifiedReviews = n())
#e
ggplot(summary_reviews, aes(x =  date, y = NumVerifiedReviews )) +
  geom_line(color = "blue") +
  labs(
    title = "Verified Reviews Over Time",
    x = "Date",
    y = "Number of Verified Reviews"
  ) +
  theme_minimal()

#d
ggplot(alexa_file, aes(x = rating, y = variation)) +
  geom_point() +
   labs(
    title = "Relationship Between Variations and Ratings",
    x = "Variation",
    y = "Rating"
  ) +
  theme_minimal() 

#the highest variations rating is Walnut Finish and Oak Finish

 
```