---
title: "RWorksheet_Sadsad#3b.Rmd"
author: "Missy Key Sadsad"
date: "2023-10-10"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: inline
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  comment = '', fig.width = 6, fig.height = 6
)
```

```{r}
library(dplyr)
```

#1. Create a data frame using the table below.
```{r}
#a.
Respondents <-  c(seq(1,20))
Sex <- c(2,2,1,2,2,2,2,2,2,2,1,2,2,2,2,2,2,2,1,2)
Father_Occupation <- c(1,3,3,3,1,2,3,1,1,1,3,2,1,3,3,1,3,1,2,1)
PersonsAtHome <- c(5,7,3,8,5,9,6,7,8,4,7,5,4,7,8,8,3,11,7,6)
SiblingsAtSchool <- c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2)
TypeOfHouses <- c (1,2,3,1,1,3,3,1,2,3,2,3,2,2,3,3,3,3,3,2)
  
data_display <- data.frame(Respondents, Sex,Father_Occupation,PersonsAtHome,SiblingsAtSchool,TypeOfHouses)
data_display
```

```{r}
#b
#in this dataset includes information from 20 respondents. It covers their gender, with 7 males and 13 females. Additionally, it records their fathers' occupations (coded as 1, 2, or 3), household sizes (ranging from 3 to 11 people), school-going siblings (ranging from 1 to 6), and the type of houses they live in (coded as 1, 2, or 3). Further analysis can reveal insights into these aspects.
summary(data_display)
```
```{r}
#c. No
```

```{r}
#d. 
data1 <- subset (data_display)[1:2, 2:6, drop=FALSE]
data1
```
```{r}
#e. 
data2 <- data_display[c(3,5), c(2,4)]
data2
```
```{r}
#f. 
types_houses <- data_display[c(6)]
types_houses
```
```{r}
#g
selected_data <- data_display %>% select(1,2,3)
data3 <- selected_data[data_display$Sex == 1,]
data3
```
```{r }
#h
selected_data2 <- data_display %>% select(1,2,5)
female <- selected_data2[data_display$SiblingsAtSchool >= 5, ]
female
```
```{r}
colnames(data_display) <- c("Respondents", "Sex", "Fathers Occupation", "Persons At Home", "Siblings At School", "Type Of Houses")
```

#2. Write a R program to create an empty data frame. Using the following codes:
```{r}
df = data.frame(Ints=integer(),

Doubles=double(), Characters=character(),
Logicals=logical(),
Factors=factor(),
stringsAsFactors=FALSE)

print("Structure of the empty dataframe:")
print(str(df))

#a.The output indicates that df is a dataframe with 0 observations (rows) and 5 variables (columns). It provides Ints, Doubles, Characters, Logicals, and Factors. The column data types and the number of levels in the factor column are also displayed.

```

3. Create a .csv file of this. Save it as HouseholdData.csv

```{r}
#a
new_Respondents <-  c(seq(1,10))
new_Sex <- c("Male","Female","Female","Male","Male","Female","Female","Male","Female","Male")
new_Fathers_Occupation <- c(1,2,3,3,1,2,2,3,1,3)
new_PersonsAtHome <- c(5,7,3,8,6,4,4,2,11,6)
new_SiblingsAtSchool <- c(2,3,0,5,2,3,1,2,6,2)
new_TypeOfHouses <- c ("Wood","Congrete","Congrete","Wood","Semi-Congrete","Semi-Congrete","Wood","Semi-Congrete","Semi-Congrete","Congrete")
  
HouseholdData <- data.frame(new_Respondents, new_Sex,new_Fathers_Occupation,new_PersonsAtHome,new_SiblingsAtSchool,new_TypeOfHouses)

library(readr)
csv_file <- "HouseholdData.csv"
write.csv(HouseholdData, file = csv_file)
HouseholdData <- read.csv("HouseholdData.csv")
```

```{r}
#b
data_display1 <- factor(HouseholdData$new_Sex, levels = c("Male" = 1, "Female" = 2))
sex_mapping <- c("Male" = 1, "Female" = 2)
data_display1<-as.integer(sex_mapping[HouseholdData$new_Sex])
unique(data_display1)
unique(HouseholdData$new_Sex)

```

```{r}
#c
data_display2 <- factor(HouseholdData$new_TypeOfHouses, levels = c("Wood" = 1, "Congrete" = 2,"Semi-Congrete" = 3)) 
sex_mapping2 <- c("Wood" = 1, "Congrete" = 2,"Semi-Congrete" = 3)
data_display2 <- as.integer(sex_mapping2[HouseholdData$new_TypeOfHouses])
unique(data_display2)
unique(HouseholdData$new_TypeOfHouses)
```

```{r}
#d
data_display3 <- factor(HouseholdData$new_Fathers_Occupation, labels = c("Farmer" = 1, "Driver" = 2,"Others" = 3))
sex_mapping3 <- c("Farmer" = 1, "Driver" = 2,"Others" = 3)
data_display3 <- as.integer(sex_mapping3[HouseholdData$new_Fathers_Occupation])
unique(data_display3)
unique(HouseholdData$new_Fathers_Occupation)
```
```{r}
#e
selected_data3 <- HouseholdData %>% select(2, 3,4)
data4 <- selected_data3[HouseholdData$new_Fathers_Occupation == 2, ]
data4
```
```{r}
#f
selected_data3 <- HouseholdData %>% select(2,6)
data4 <- selected_data3[HouseholdData$new_SiblingsAtSchool >= 5,]
data4
```



```{r}
colnames(HouseholdData) <- c("Respondents", "Sex", "Fathers Occupation", "Persons At Home", "Siblings At School", "Type Of Houses")
```







4. Interpret the Graph.
 
  In the bar graph titled "Sentiment of Tweets per Day," it have three distinct sentiment categories: Negative, Neutral, and Positive. Each category represents the prevailing mood and tone of the tweets on specific dates in July 2020. 

 Negative Sentiment: This represents tweets expressing dissatisfaction, criticism, or negative emotions. On specific dates like July 15 and July 21, 2020, negative tweets surged, indicating intense discussions or concerns.

Neutral Sentiment: These tweets strike a balanced tone, presenting information objectively. Across various days in July 2020, including July 14, 15, 17, 18, and 21, neutral sentiments prevailed, reflecting varying levels of non-partisan discourse.

Positive Sentiment: This category showcases optimistic, enthusiastic, and positive tweets. Despite negative sentiments on certain days, like July 14, 15, 17, 18, and 21, positive tweets also shone, symbolizing resilience, hope, or a positive outlook amid diverse sentiments.

In summary, this graph succinctly captures Twitter's sentiment landscape in July 2020, highlighting fluctuations in Negative, Neutral, and Positive sentiments on specific dates.

 
#hello, ma'am! naka chunk output-inline ko ma'am so idk if pwede ni siya, but muna lg gn gamit ko para diri na mag-gwa sa source code iya output ma'am, para isa nalang d nko mag copy kung ano ma gwa sa console... ~.~ 










