---
title: "RWorksheet_5"
author: "BSIT-2B"
date: "2023-12-10"
output:
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
# I PUT THIS MAAM BECAUSE I CAN'T KNIITED IT IN PDF
options(repos = c(CRAN = 'https://cloud.r-project.org/'))
install.packages("AppliedPredictiveModeling")
```
 
##Basic Statistics

#1. Create a data frame for the table below. Show your solution.

```{r}
students_score <- data.frame (
  Students = c(1,2,3,4,5,6,7,8,9,10),
  preTest =  c(55,54,47,57,51,61,57,54,63,58),
  postTest = c(61,60,56,63,56,63,59,56,62,61)
)
students_score
#a. Compute the descriptive statistics using different packages (Hmisc and pastecs).Write the codes and its result
library(Hmisc)
library(pastecs)

stats_hmisc <- describe(students_score)
stats_hmisc
stats_pastics <- stat.desc(students_score)
stats_pastics
```

##2. The Department of Agriculture was studying the effects of several levels of a fertilizer on the growth of a plant. For some analyses, it might be useful to convert the fertilizer levels to an ordered factor.
```{r}
#a. Write the codes and describe the result.
order_fertilize <- c(10,10,10, 20,20,50,10,20,10,50,20,50,20,10)
ordered(order_fertilize)
# the data_fertilize result shows the level as an ordered factor.
```

##3. Abdul Hassan, president of Floor Coverings Unlimited, has asked you to study the ex-ercise levels undertaken by 10 subjects were “l”, “n”, “n”, “i”, “l” , “l”, “n”,“n”, “i”, “l” ; n=none, l=light, i=intense.

```{r}
# a. What is the best way to represent this in R?
exe_levels <- c("l", "n", "n", "i", "l", "l", "n", "n", "i", "l")
exe_factor <- factor(exe_levels, levels = c("n", "l", "i"), labels = c("none", "light", "intense"))
exe_factor
```

## 4. Sample of 30 tax accountants from all the states and territories of Australia and their individual state of origin is specified by a character vector of state mnemonics as:

```{r}

#a. Apply the factor function and factor level. Describe the results.
#the factor_with_level variable result is factor with level.

aussie_state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld",
           "vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt",
           "wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw",
           "vic", "vic", "act")
aussie_state

factor_and_level <-factor(aussie_state, levels = c("act", "nsw", "nt", "qld", "sa", "tas", "vic", "wa"))  
factor_and_level
```

##5. From #4 - continuation:
 
```{r}
aussie_incomes <- c(60, 49, 40, 61, 64, 60, 59, 54,
             62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48,
             65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
aussie_incomes

# a. Calculate the sample mean income for each state we can now use the special function tapply():

incmeans <- tapply(aussie_incomes, factor_and_level, mean)
incmeans
# b. Copy the results and interpret.
#The result has the means of each states that has factor with levels 
 
 

```


##6. Calculate the standard errors of the state income means (refer again to number 3) 
```{r}

#stdError <- function(x) sqrt(var(x)/length(x)) Note: After this assignment, the standard errors are calculated by: incster <- tapply(incomes, statef, stdError)

#a. What is the standard error? Write the codes.
stdErrors <- function(x) sqrt(var(x)/length(x))
stdErrors
incster <- tapply(aussie_incomes, factor_and_level, stdErrors)
incster

#b. Interpret the result.
#It displays the state income means' computed standard errors. The sample mean income is a reasonably accurate estimate of the genuine population mean income for that state if the standard error of the state income mean is modest. A big standard error indicates less accuracy in predicting the underlying population mean and greater variability in the sample mean.

```


```{r}
#7. Use the titanic dataset.

#a. subset the titatic dataset of those who survived and not survived. Show the codes and its result.
library(datasets)
data(Titanic)

Titanic<-as.data.frame(Titanic)

subset_titanic<-subset(Titanic, Survived=="Yes")
subset_titanic
not_subset_titanic<- subset(Titanic, Survived == "No")
not_subset_titanic
```

##8. The data sets are about the breast cancer Wisconsin. The samples arrive periodically as Dr. Wolberg reports his clinical cases.  

```{r}
library(readr)
csv.file<-"breastcancer_wisconsin.csv"
breastcancer_wisconsin<-read.csv("breastcancer_wisconsin.csv")
breastcancer_wisconsin
summary(breastcancer_wisconsin)

#a. describe what is the dataset all about.
#It displays the state income means' computed standard errors. The sample mean income is a reasonably accurate estimate of the genuine population mean income for that state if the standard error of the state income mean is modest. A big standard error indicates less accuracy in predicting the underlying population mean and greater variability in the sample mean.

#d. Compute the descriptive statistics using different packages. Find the values of:

#d.1 Standard error of the mean for clump thickness.
clumpThickness_dataset <- breastcancer_wisconsin$clump_thickness
stdError_clump_thickness <- stdErrors(clumpThickness_dataset)
stdError_clump_thickness


#d.2 Coefficient of variability for Marginal Adhesion.
marginalAdhesion_data <- breastcancer_wisconsin$marginal_adhesion
mean <- mean(marginalAdhesion_data)
sd <- sd(marginalAdhesion_data)
cv <- sd / mean
cv
cv<-cv*100 #getting the percentage
cv

#d.3 Number of null values of Bare Nuclei.
bareNuclei_data <- breastcancer_wisconsin$bare_nucleoli
numNull__values <- sum(is.na(bareNuclei_data))
numNull__values

#d.4 Mean and standard deviation for Bland Chromatin
blandChromatin_data <- breastcancer_wisconsin$bland_chromatin
mean_blandChromatin <- mean(blandChromatin_data)
sd_blandChromatin <- sd(blandChromatin_data)
mean_blandChromatin
sd_blandChromatin

#d.5 Confidence interval of the mean for Uniformity of Cell Shape
#Using t.test function
shapeUniformity_data <- breastcancer_wisconsin$shape_uniformity
confidence_Interval <- t.test(shapeUniformity_data, na.rm = TRUE)$conf.int
confidence_Interval

#d. How many attributes?
length(breastcancer_wisconsin)
names(breastcancer_wisconsin)

#e. Find the percentage of respondents who are malignant. Interpret the results
percentage_malignant <- sum(breastcancer_wisconsin$class == 4) / nrow(breastcancer_wisconsin) * 100
percentage_malignant

#Accordingly, the result 34.47783 indicates that roughly 34.48% of the participants in the dataset on breast cancer are categorized as malignant. The relative frequency of malignant cases in the dataset is shown by this percentage.
```
##9. Export the data abalone to the Microsoft excel file. Copy the codes.
```{r}
library("AppliedPredictiveModeling")
data("abalone")
View(abalone)
head(abalone)
summary(abalone)

abalone_excel<-"C:/Users/missy/OneDrive/Documents/Github/RWorksheets_Sadsad/Worksheet#5/abaloneData.xlsx"
install.packages("writexl")
library(writexl)
write_xlsx(abalone, abalone_excel)
```